%-------------------------
% Resume in Latex
% Author : Adam Silva
% Adapted from: Sourabh Bajaj
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

% Just in case someone needs a heading that does not need to be in a list
\newcommand{\resumeHeading}[4]{
    \begin{tabular*}{0.99\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeText}[1]{
    #1 \\
    \vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
    \textbf{\Large Adam Lucas Pinheiro da Silva}  &  LinkedIn : \href{https://www.linkedin.com/in/adamlucax/}{\color{blue}\underline{adamlucax}}\\
    \href{mailto:adam.lucax@gmail.com}{\color{blue}adam.lucax@gmail.com}    % &  GitHub : \href{https://github.com/adamlucax}{\color{blue}\underline{adamlucax}}\\
                                                                                                                 &  Mobile : \href{tel:+5579991054252}{+55 79 99105 4252}\\
                                                                                                                 &  Aracaju, BR 
\end{tabular*}\vspace{-5pt}


%--------------ABOUT--------------------

\section{About}
  \resumeText 
    {Software Engineer with almost 10 years programming and 5 years developing games professionally, applying my knowledge in clean code and design patterns. Also passionate about architecting new features, creating tools, and solving problems with data structures and algorithms}

%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Universidade Federal de Sergipe}{Aracaju, BR}
      {Bachelor of Computer Science (Forming)}{Jun 2024}
  \resumeSubHeadingListEnd

%--------PROGRAMMING SKILLS------------
\section{Skills}
  \resumeSubHeadingListStart
    \item{
      \textbf{Languages}{: C\#, Python}
      \hfill
      \textbf{Technologies}{: Unity, Git, AWS, TeamCity}
    }\vspace{-5pt}
    \item{
      \textbf{Programming}{: Clean Code, SOLID, Design Patterns, Data Structure, Algorithms, Optimization}
    }\vspace{-5pt}
  \resumeSubHeadingListEnd

%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Lumen Games}{Aracaju, BR}
      {Software Engineer}{Apr 2021 - Present}
      \resumeItemListStart
        \resumeItem
          {\href{https://play.google.com/store/apps/details?id=games.lumen.homatales}{\color{blue}\underline{Dreamweaver Tactics}}}
          {An strategic autobattle game using hex grid.
            \begin{itemize}
              \item Worked closely with game designers to develop the initial prototype and iteratively refine game mechanics.
              \item Held a engineering role throughout the project lifecycle, from pre-production to MVP launch. Contributed to risk analysis, and conducted revisions to reutilize our codebase modules.
              \item Collaborated in building the programming team, from conducting technical interviews to onboarding new hires.
              \item Designed and implemented a data structure to facilitate hex grid generation, streamline UI input snapping, and grid-based pathing.
              \item Developed a scalable architecture for managing character abilities and skills, enabling integration of multiple status effects and enhancing designers configuration.
            \end{itemize}
          }
        \resumeItem
          {\href{https://play.google.com/store/apps/details?id=games.redhood.hempparadise}{\color{blue}\underline{Hemp Paradise: City Building}}}
          {A game to build your own weed resort.
            \begin{itemize}
              \item Worked collaboratively on the development of a player's building editing tool using Unity's Isometric Tilemap.
              \item Owned the development of a multiplayer guild event feature, leveraging backend API integration and close collaboration with backend engineers.
              \item Implemented the only minigame, that revolving around squared grid navigation, applying some data structures and pathing algorithms.
              \item Partnered with external sound engineers to import and integrate audio assets into the game using WWise.
              \item Managed the import and integration of assets using Spine and sprites.
              \item Managed the integration and updates of various SDKs including Firebase, DeltaDNA, IronSource, and others.
            \end{itemize}
          }
        \resumeItem
          {\href{https://play.google.com/store/apps/details?id=com.eastsidegames.thegoldbergs}{\color{blue}\underline{The Goldbergs: Back to the 80s}}}
          {An idle game based on \textit{The Goldbergs} TV series.
            \begin{itemize}
              \item Collaborated on refining and optimizing our proprietary tool to import data from with Google Spreadsheets using Python.
              \item Integrated an external framework tailored for idle games.
              \item Implemented a map generation system based on designer-provided configurations.
            \end{itemize}
          }
      \resumeItemListEnd

    \resumeSubSubheading
     {Software Engineer - Intern}{Feb 2019 - Apr 2021}
     \resumeItemListStart
        \resumeItem
          {\href{https://www.youtube.com/watch?v=MLjikLDk6D8&ab_channel=LumenGames}{\color{blue}\underline{Kids Vs Zombies}}}
          {A grid based strategic roguelike game.
            \begin{itemize}
              \item Developed and fine-tuned adaptive UI screens to ensure seamless user experience across various aspect ratios.
              \item Identified and resolved software bugs to ensure optimal functionality and user experience.
              \item Conducted refactoring efforts aimed at scaling the codebase to evolving project features.
            \end{itemize}
          }
     \resumeItemListEnd


% -----------PROJECTS-----------------
\section{Personal Projects}
    \resumeSubItem{Problem Solving}
      {Used some platforms such as LeetCode, HackerRank, and Codeforces to solve some algorithmic problems as hobby. Additionally, I have actively participated in ICPC regional contests.}
    \resumeSubItem{Programming Teacher}
      {Worked teaching some kids in middle school to code, to stimulate kids to participate in the Brazilian Olympiad in Informatics}
    % \resumeSubItem{Unreal Project}
    % {Party Game}
%     \resumeSubItem{Godot Project}
%       {Data Visualization of Git Log data using D3 to analyze project trends over time.}
%     \resumeSubItem{C++ Project}
%       {Pixel Perfect}

\resumeSubHeadingListEnd
\end{document}